### 2014-10-08 fundamentals/examples.tex
discuss pu buildup data

The \Class{Source} and \Class{Sink} modules from \Cycamore were also used as a
source of fresh, enriched uranium and a repository respectively. A simple
custom recycled fuel fabrication facility was used.  This fabrication facility
mixes fissile and fertile streams to match target fuel compositions as closely
as possible.  The method used for this matching is approximately the same as
that used by the Cosi fuel cycle simulator \TODO{cite COSI equivalence
method}. The material flows for this simulation are shown below in figure
\ref{fig:flow-modopen}.

\begin{figure}[!]
\label{fig:flow-modopen}
\caption{Modified open 1-pass MOX recycle fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\end{figure}

@@

This results in new the material flows in Figure \ref{fig:flow-closed}. Note
that because the \Class{BatchReactor} always transmutes fuel into the same
composition, the nuclide level flows are not very realistic for the full, multipass
recycle case.

\begin{figure}[!]
\label{fig:flow-closed}
\caption{Full MOX recycle (multi-pass) fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-closed-1.eps}
\end{center}
\end{figure}

\TODO{discuss Pu buildup charts}

\begin{figure}[!]
\label{fig:puseries-1}
\caption{bla}
\begin{center}
\includegraphics{./images/puseries-1.eps}
\end{center}
\end{figure}

\begin{figure}[!]
\label{fig:puseries-n}
\caption{bla}
\begin{center}
\includegraphics{./images/puseries-n.eps}
\end{center}
\end{figure}

>>>>

The \Class{Source} and \Class{Sink} modules from \Cycamore were also used as a
source of fresh, enriched uranium and a repository respectively. A simple
custom recycled fuel fabrication facility was used.  This fabrication facility
mixes fissile and fertile streams to match target fuel compositions as closely
as possible.  The method used for this matching is approximately the same as
that used by the Cosi fuel cycle simulator \TODO{cite COSI equivalence
method}. The material flows for this simulation are shown below in figure
\ref{fig:flowmodopen}.

\begin{figure}[H]
\label{fig:flowmodopen}
\caption{Modified open 1-pass MOX recycle fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\end{figure}

@@

This results in new the material flows in Figure \ref{fig:flowclosed}. Note
that because the \Class{BatchReactor} always transmutes fuel into the same
composition, the nuclide level flows are not very realistic for the full, multipass
recycle case.

\begin{figure}[H]
\label{fig:flowclosed}
\caption{Full MOX recycle (multi-pass) fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-closed-1.eps}
\end{center}
\end{figure}

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
(no recycle), modified open, and closed (infinite-pass recycle) variations of
the scenario described above (all just a single reactor).  The figure was
generated directly from \Cyclus output data. After several batch cycles (near
month 300) in the modified open and closed cases, enough separated fissile
material accumulates in the fuel fabrication facility to generate a full
recycled batch.  When this batch is transmuted, more plutonium is burned than
created.  This results in a drop in the total fuel cycle system plutonium
inventory.  This pattern repeats roughly every 10 cycles (200 months) for the
modified open case and every 9 cycles (180 months) for the closed case.
Because the modified open scenario does not re-recycle material, it takes the
fabrication facility 1 cycle longer to accumulate a full batch worth of
fissile material.  Because facilities are represented individually and
transact discrete materials as discrete events, realistic non-uniform patterns
in facility behavior can be observed affecting total system behavior in ways
that are less commonly observed in fleet-based, continuous material flow
modeling.

\begin{figure}[H]
\label{fig:puseries1}
\caption{System plutonium buildup with one reactor.}
\begin{center}
\includegraphics{./images/puseries-1.eps}
\end{center}
\end{figure}

The open, modified open, and closed scenarios can easily be modified to have
several reactors each with staggered refueling times.  As the number of
reactors increases, the behavior of the system approaches a more steady
average reminiscent of continuous material flow models.  The plutonium buildup
for these three multi-reactor variations is shown in Figure
\ref{fig:puseriesn}.

\begin{figure}[H]
\label{fig:puseriesn}
\caption{System plutonium buildup with staggered refueling for many reactors.}
\begin{center}
\includegraphics{./images/puseries-n.eps}
\end{center}
\end{figure}
